%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{snizami-resume}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{academicons}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{SAQIB}{NIZAMI}{
\urlstyle{same}
\href{https://snizami.com}{\faLink \space snizami.com} |
\href{mailto:snizami@gmail.com}{\faEnvelope \space snizami@gmail.com} | 
\faPhone \space 646 236 8570 | \faGlobe \space {New York, NY}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.26\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Programming}
% \location{Over 5000 lines:}
Python\textbullet{}PySpark\textbullet{}SQL\textbullet{}\\
JavaScript(Node.js, Sequelize)\textbullet{}\\
R\textbullet{}Shell\textbullet{}\LaTeX
\sectionsep

\subsection{Infra + DevOps}
AWS\textbullet{}GCP\textbullet{}Aptible\textbullet{}\\
Docker\textbullet{}CloudFormation\textbullet{}\\
Terraform\textbullet{}Github Actions
\sectionsep

\subsection{Data Engineering}
PostgreSQL\textbullet{}Snowflake\textbullet{}dbt\textbullet{}\\
redis\textbullet{}Airflow\textbullet{}GraphQL\textbullet{}\\ 
AWS: Lambda, Kinesis, EKS\textbullet{}\\
REST API\textbullet{}ETL System Design
\sectionsep

\subsection{Data Science}
Pandas\textbullet{}Jupyter\textbullet{}Numpy\textbullet{}\\
Scikit-Learn\textbullet{}Tensorflow\textbullet{}\\
Keras\textbullet{}nltk\textbullet{}spaCy\textbullet{}\\
statsmodels\textbullet{}imbalanced-learn
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 

\href{https://github.com/saqibnizami}{\faGithub: \bf saqibnizami} \\
\href{https://www.linkedin.com/in/saqibnizami}{\faLinkedin: \bf saqibnizami} \\
\href{https://www.researchgate.net/profile/Saqib-Nizami/publications}{\aiResearchGateSquare: \bf Publications}
\sectionsep

\section{Projects}

\subsection{Interpretable \\
Breast Cancer \\
Classification \\
using Custom CNN}
\descript{Capstone. Data Science Immersive}
\location{Apr 2018 - Jul 2018}
% \vspace{\topsep} 
% \begin{tightemize}
Developed custom Convolutional Neural Network in TensorFlow based on breast cancer cells. Augmented histology image dataset using GPU-enabled GCE and AWS instances. Investigated model interpretability using LIME.
% \end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{General Assembly}
\descript{Data Science Immersive Certification}
% \descript{Data Science Immersive}
\location{New York, NY}
\sectionsep

\subsection{R.I.T.}
% \descript{Rochester Institute of Technology}
\descript{BS, Biomedical Science}
\location{Rochester, NY}
College of Science \\
Presidential Merit Scholar\\
\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.72\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{ZipDrug (acq. Anthem, Inc.)}
\descript{| Engineer III, Data Team Lead}
\location{Oct 2019 - Present | Jersey City, NJ}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Maintained legacy PySpark ETL, PostgreSQL RDS, Python codebase, and Looker (lookml) code.
\item Expanded Data Engineering and Reporting team by hiring and mentoring engineers and analysts.
\item Architected and implemented new scalable solutions to replace legacy code and infrastructure. Utilized Airflow and AWS Elastic Kubernetes Service to orchestrate PySpark ETL and downstream Python/JavaScript data processes.
\item Implemented two business program expansions that resulted in tripling of data volume to several hundred-thousand patients and millions of claims.
\item Spearheaded Snowflake data warehouse using dbt to build Data Marts. Developed the POC and led Data Warehouse team in Production-level warehousing efforts.
\item Created internal reporting dashboards for business teams, investor and executive-level reports, and client-facing reports on program performance.
\item Worked on Digital Integration with Anthem's Sydney HealthCare app. Deployed architecture to enable file transfers between Anthem-IngenioRX and Zipdrug teams. Designed and implemented backend application to provide Zipdrug enrollment and status information to Kinesis Data Stream using asynchronous python producer/consumer pattern.
\end{tightemize}
\sectionsep

\runsubsection{General Assembly}
\descript{| Python Instructional Associate }
\location{Sep 2019 - Dec 2019 | New York, NY}
\begin{tightemize}
\item Evening Python Programming Class instructor. Taught basic Python Programming (Data Structures, Working with APIs, Analysis with pandas).
\end{tightemize}
\location{Oct 2018 and Jun 2019 | New York, NY}
\begin{tightemize}
\item Taught Python Data Analysis (Basic Data Structures, pandas, matplotlib/seaborn) to an enterprise client: UTC dX.
\end{tightemize}
\sectionsep

\runsubsection{uBiome}
\descript{| Data Scientist, Analytics }
\location{Oct 2018 – Jul 2019 | New York, NY}
\begin{tightemize}
\item Developed a statistically balanced Random Forest classification model. Created an API to serve model outputs in production.
\item Designed and deployed internal python-based dashboarding platform for Data Analytics Team.
\item Used Latent Dirichlet Allocation on customer NPS feedback to identify pain
points in the customer journey. Wrote ETL to obtain data from Wootric API.
\item Implemented dockerized workflow for the Analytics Team.
\item Created ETL for Google Ads and Facebook Ads and maintained analytics team PostgreSQL DB.
\end{tightemize}
\sectionsep

\runsubsection{Memorial Sloan Kettering Cancer Center}
\descript{| Sr. Research Associate}
\location{Sep 2017 - Jan 2018 | New York, NY}
\begin{tightemize}
\item Utilized R and Bioconductor to analyze RNA Sequencing data from tumor cell biopsies
\end{tightemize}
\sectionsep

\runsubsection{Columbia University Medical Center}
\descript{| Sr. Research Technician}
\location{Jul 2010 - Jul 2017 | New York, NY}
\begin{tightemize}
\item Established quantifiable functional osteoclast imaging \textit{in vivo} using fluorescent signal analysis. Work published in \textit{Cell} and \textit{Journal of Biophotonics}.
\item Conducted and analyzed \textit{in vivo} and \textit{in vitro} dose response/kinetic release curve experiments for novel cancer therapeutic delivery mechanisms.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
